MSDS 7333 Case Study 06

### 2017-06-20 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Minor Corrections. I will work on this throughout tomorrow.
Adding 2.3 material from Ben's update

Now, we analyze our three scenarios for both APs included, rejectedAP left out, and then chosenAP left out. Three neighbors were used for three angles. The accuracy for each scenario as determined by the sum of squares difference between estimated X,Y and actual X,Y were outputted as well. Cross-validation was not used at this time.

@@

## 2.3: Weighted K-Nearest Neighbors {#WtKNN}

>>>>

Now, we analyze our three scenarios for both APs included, rejectedAP left out, and then chosenAP left out. Three neighbors were used for three angles. The accuracy for each scenario as determined by the sum of squares difference between estimated X,Y and actual X,Y were output as well. Cross-validation was not used at this time.

@@

## 2.3: Weighted K-Nearest Neighbors {#WtKNN}
In this exercise, we investigated using an alternative k-nearest prediction method using the weighted 
K-nearest neighbors approach.  The calculation of the Euclidean distance error was found to be 1194, whereas the Mean SS error was found to be 210.  The Euclidean distance weighted k-nearest neighbors 
method had the highest error, while the Mean SS weighted K-nearest neighbors method had the smaller
error.

| k |Euclidean distance error|Mean SS error|
|:-:|:-----------------:|:-----------------:|
| |1194|210|
